\textbf{Analyzing Machupo virus-receptor binding by molecular dynamics simulations}

### 2014-01-06 paper.tex
copy edit

Again, the NAMD configuration file is made available via github \\ (https://github.com/clauswilke/MACV\_SMD). We used a similar configuration to that in equilibration. One significant difference was to make a cubic water box with a side length equal to the long axis of the complex plus a 10~\AA\  buffer on either side, and simply restrict center of mass motion with the NAMD setting. This was done to avoid affecting the system energy while calculating free energy differences.

@@

The statistical package R was used for all further analysis and visualization. Each of the 50 independent trajectories per mutant produced a fairly noisy force curve. The force curves for each mutant were smoothed by using the smooth.spline() and predict() functions in R with default settings over all replicates as in Figure~\ref{fig:force_curve}. The two primary descriptive statistics we used were maximum interpolated applied force and total area under the interpolated curve (AUC). We tested for signifiant differences in maximum force or AUC by carrying out t tests for all pairwise combinations (each mutant compared to each other mutant), using the pairwise.t.test() function in R. We adjusted p values to correct for multiple testing using the False-Discovery-Rate (FDR) method \citep{BenjaminiHochberg1995}. The ggplot \citep{ggplot} package was used to generate most of the figures.

@@

Before systematically applying SMD to the GP1/hTfR1 interaction, we needed to ensure the method was sufficiently sensitive to distinguish between relatively minor point mutations. While SMD has been applied previously to measure the binding energy of high-affinity T-cell receptor interactions \citep{Cuendet2008,Cuendet2011}, to our knowledge the method has never been used previously to parse small differences in a complex energy landscape. For this initial sensitivity analysis, we tested alanine substitutions congruent with the traditional experimental and computational approach.

>>>>

Again, the NAMD configuration file is made available via github (https://github.com/clauswilke/MACV\_SMD). We used a similar configuration to that in equilibration. One significant difference was to make a cubic water box with a side length equal to the long axis of the complex plus a 10~\AA\  buffer on either side, and simply restrict center of mass motion with the NAMD setting. This was done to avoid affecting the system energy while calculating free energy differences.

@@

The statistical package R was used for all further analysis and visualization. Each of the 50 independent trajectories per mutant produced a fairly noisy force curve. {\color{red}\emph{This is not entirely clear. I thought there is only one approach now.} The force curves for each mutant were smoothed either by using the smooth.spline() and predict() functions in R with default settings over all replicates as in Figure~\ref{fig:force_curve}. The latter approach was used for statistical analysis.} The two primary descriptive statistics we used were maximum interpolated applied force and total area under the interpolated curve (AUC). We tested for signifiant differences in maximum force or AUC by carrying out t tests for all pairwise combinations (each mutant compared to each other mutant), using the pairwise.t.test() function in R. We adjusted p values to correct for multiple testing using the False-Discovery-Rate (FDR) method \citep{BenjaminiHochberg1995}. The ggplot \citep{ggplot} package was used to generate most of the figures.

@@

Before systematically applying SMD to the GP1/hTfR1 interaction, we needed to ensure the method was sufficiently sensitive to distinguish between relatively minor point mutations. While SMD has been applied previously to measure the binding energy of high-affinity T-cell receptor interactions \citep{Cuendet2008,Cuendet2011}, to our knowledge the method has never been used previously to parse small differences in a complex energy landscape. {\color{red}\emph{$\leftarrow$ Is this still a correct statement? I know we deleted a novelty claim earlier in the ms.}} For this initial sensitivity analysis, we tested alanine substitutions congruent with the traditional experimental and computational approach.
